Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-09-27 manuscript.Rmd
recomend changelog

We would like to note that in the PAC paradigm, the direct comparison of the preregistration and the final publication is particularly easy to accomplish.
Because there is a single unambiguous reference point, that is the dynamic document, including code, under version control, changes can be inspected by authors and readers alike.
To make the comparison even more accessible, we highly recommend that the authors review all changes made to the preregistered plan to summarize and justify them for their reader, e.g. in the discussion of the final manuscript [^summarize-changes].
The reader is also in a position to inspects the changes one by one and can therefore make an informed judgment about their implications for the inferences drawn.

>>>>

We would like to note that in the PAC paradigm, the direct comparison of the preregistration and the final publication is particularly easy to accomplish.
Because there is a single unambiguous reference point, that is the dynamic document, including code, under version control, changes can be inspected by authors and readers alike.
Authors should at least review all changes made to the preregistered plan to summarize and justify them for their reader, e.g. in the discussion of the final manuscript [^summarize-changes].
Such retrospective summary already serves to put changes into context, however, a change log that is kept continually and where changes are explained when they are made, provides more immediate and detailed information.
Each entry in the change log should contain the commit id to the respective changes.
The reader is also in a position to inspects the changes one by one and can therefore make an informed judgment about their implications for the inferences drawn.
